Clean 2015 Raw Data

### 2017-08-25 data-raw/Clean_Data_and_Calculate_AUDPS.Rmd
Cleanup in RAW_data
Remove extra files and add documentation to file about the cleaning

The raw data are located in the `extdata` folder of the installed
_rice.awd.pests_ and can be accessed using:

@@

save(DS2015, file = "../data/DS2015", compress = "bzip2")

```

The raw data are located in the `extdata` folder of the installed
_rice.awd.pests_ and can be accessed using:
```{r, eval=FALSE}
load(system.file("extdata", "DS2016_Raw_1.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2016_Raw_2.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2016_Raw_3.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2016_Raw_4.csv", package = "rice.awd.pests"))
```

@@

@@

# add column with midpoint % tiller ShB severity -------------------------------

RAW_data <-
  dplyr::mutate(
    RAW_data,
    PERC_TIL_ShB = dplyr::case_when(
      TIL_ShB == 0 ~ 0,
      TIL_ShB == 1 ~ 1,
      TIL_ShB == 2 ~ 2.5,
      TIL_ShB == 3 ~ 10,
      TIL_ShB == 4 ~ 32.5,
      TRUE ~ 75
    )
  )

@@

TShB_percent_AUDPS <-
  audps(evaluation = TShB_perc_wide[, 2:6],
        dates = as.vector(TShB_perc_15[1:5, 6]))

LShB_percent_AUDPS <-
  audps(evaluation = LShB_perc_wide[, 2:6],
        dates = as.vector(LShB_perc_15[1:5, 6]))

@@

save(AUDPS, file = "../data/AWD_AUDPS", compress = "bzip2")
```

>>>>

The raw data are located in the `extdata` folder of the installed
_rice.awd.pests_

# Dry season 2015 importing and cleaning

DS2015 data can be accessed using:

@@

if (!dir.exists("../data")) {
  dir.create("../data", recursive = TRUE)
}
```

# Dry season 2016 importing and cleaning

The 2016 season raw data are located in the `extdata` folder of the installed
_rice.awd.pests_ and can be accessed using:

```{r, eval=FALSE}
load(system.file("extdata", "DS2016_Raw_1.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2016_Raw_2.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2016_Raw_3.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2016_Raw_4.csv", package = "rice.awd.pests"))
```

@@

# Calculating Area Under the Disease Progress Stairs (AUDPS)

Because the data were collected on an ordinal scale, but not evenly spaced,
the data are converted to the midpoint value of the percent range for severity
and then the AUDPS is calculated from that. See lines 544 and 559 for this.

After that the AUDPS is calculated using functionality from the _agricolae_
package.

Last, the data are saved in the package for use analysis, which is detailed
in the package [vingettes](../vignettes).

@@

# add column with midpoint % tiller ShB severity -------------------------------
RAW_data <-
  dplyr::mutate(
    RAW_data,
    PERC_TIL_ShB = dplyr::case_when(
      TIL_ShB == 0 ~ 0,
      TIL_ShB == 1 ~ 1,
      TIL_ShB == 2 ~ 2.5,
      TIL_ShB == 3 ~ 10,
      TIL_ShB == 4 ~ 32.5,
      TRUE ~ 75
    )
  )

@@

TShB_percent_AUDPS <-
  agricolae::audps(evaluation = TShB_perc_wide[, 2:6],
        dates = as.vector(TShB_perc_15[1:5, 6]))

LShB_percent_AUDPS <-
  agricolae::audps(evaluation = LShB_perc_wide[, 2:6],
        dates = as.vector(LShB_perc_15[1:5, 6]))

@@

devtools::use_data(AUDPS,
                   compress = "bzip2",
                   overwrite = TRUE)
```
